### 2022-03-15 paper/ase22/approach.tex
add table script
debugging

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/overview.pdf}
  \caption{Overview of \tool{}.}
  \label{fig:overview}
\end{figure*}

\sw{Some paragraphs in this overview part should go earlier in the
  paper. I am just writing them here for now as I don't think we have
  them in the intro/background yet.}  We design and implement
\emph{Specification- and Syntax-based Linguistic Capability Testing
  (\tool{})} to automatically generate test cases to test the
robustness of sentiment analysis models. We identify four goals for a
large and effective test suite:

@@

We present \tool{}, a new linguistic capability test case generation
tool, that satisfies all of these criteria.  \sw{I could not summarize
  a cohesive idea that drives our design. Leaving it here to fill in.
  Also, I felt my writing below still lacks justification for some
  design choices (e.g., why we do the differentiation).}  Figure
\ref{fig:overview} shows the overview of \tool{}, which consists of
two phases.  The \emph{specification-based seed generation} phase
performs rule-based searches from a real-world dataset ({\bf G1}) and
template-based transformation to obtain the initial seed sentences.
The search rules (e.g., search for neutral sentences that do not
include any positive or negative words) and transformation templates
(e.g., \sw{add an example}) are defined in the \emph{linguistic
  capability specifications}, which guarantee that each resulting seed
conforms to a specific linguistic capability ({\bf G3}) and is
labelled correctly ({\bf G4}).

@@

Table \ref{tab:specification} shows the search rules and the
transformation templates of all 11 linguistic capabilities we
implemented in \tool{}. \sw{will revise the rest of 3.1 after talking
  to Jaeseong... I think we can show all the specifications.}

\begin{table*}[t]
\small
\centering
\begin{tabular}{l|l}
  {\bf Linguistic capability}	 & {\bf Search rule and transformation template}\\
  \hline
  LC1: Short sentences with neutral & search: \{length: <10; include: neutral adjs \& neutral nouns; \\
  adjectives and nouns & exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}  \\
  & transform: - \\
  \hline
  LC2: Short sentences with  & search: \{length: <10; include: pos adjs; exclude: neg adjs \& neg verbs \& neg nouns; label: pos\} \\
  sentiment-laden adjectives  & | \{length: <10; include: neg adjs; exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}  \\
  & transform: - \\
  \hline
  LC3: Sentiment change over time, & search: \{label: pos\} | \{label: neg\} \\
  present should prevail & transform: \\
  \hline
  LC4: Negated negative should be & search: \{start: [This, That, These, Those] X [is, are]; label: neg\} \\
  positive or neutral & transform:  \\
  \hline
  LC5: Negated neutral should & search: \{start: [This, That, These, Those] X [is, are]; label: neutral\} \\
  still be neutral & transform: \\
  \hline
  LC6: Negation of negative at the & search: \{label: neg\} \\
  end, should be positive or neutral & transform: \\
  \hline
  LC7: Negated positive with neutral & search: \{length: <20; label: pos\} | \{length: <20; label: neutral\} \sw{Not sure about this rule.} \\
  content in the middle & transform: \\
  \hline
  LC8: Author sentiment is more & search: \{label: pos\} | \{label: neg\} \\
  important than of others & transform: \\
  \hline
  LC9: parsing sentiment in & search: \{label: pos\} | \{label: neg\} \\
  (question, yes) form & transform: \\
  \hline
  LC10: Parsing positive sentiment & search: \{label: pos\} \\
  in (question, no) form & transform: \\
  \hline
  LC11: Parsing negative sentiment & search: \{label: neg\} \\
  in (question, no) form & transform: \\
  \hline
\end{tabular}
\caption{Search rules and transformation templates for linguistic capabilities. \sw{Add transformation templates. May need to find a better specification language.}}
\label{tab:specification}
\end{table*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/overview.pdf}
  \caption{\OverviewFigCaption}
\end{figure*}

\sw{Some paragraphs in this overview part should go earlier in the
  paper. I am just writing them here for now as I don't think we have
  them in the intro/background yet.}  We design and implement
\emph{Specification- and Syntax-based Linguistic Capability Testing
  (\tool)} to automatically generate test cases to test the
robustness of sentiment analysis models. We identify four goals for a
large and effective test suite:

@@

We present \tool{}, a new linguistic capability test case generation
tool, that satisfies all of these criteria.  \sw{I could not summarize
  a cohesive idea that drives our design. Leaving it here to fill in.
  Also, I felt my writing below still lacks justification for some
  design choices (e.g., why we do the differentiation).}
Figure~\ref{fig:overview} shows the overview of \tool{}, which
consists of two phases.  The \emph{specification-based seed
  generation} phase performs rule-based searches from a real-world
dataset ({\bf G1}) and template-based transformation to obtain the
initial seed sentences.  The search rules (e.g., search for neutral
sentences that do not include any positive or negative words) and
transformation templates (e.g., \sw{add an example}) are defined in
the \emph{linguistic capability specifications}, which guarantee that
each resulting seed conforms to a specific linguistic capability ({\bf
  G3}) and is labelled correctly ({\bf G4}).

@@

Table~\ref{tab:specification} shows the search rules and the
transformation templates of all 11 linguistic capabilities we
implemented in \tool{}. \sw{will revise the rest of 3.1 after talking
  to Jaeseong... I think we can show all the specifications.}

\InputWithSpace{tables/lc-requirement-table}
